### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Many thanks for your positive comments on the strength of our paper and the novelty of the proposed attack method.}

%%%% 问题 1.1 %%%%
\textit{In addition, I suggest the authors add more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. The experimental results show that it is effective to use the predicted boxes instead of ground truth boxes for training perturbations.}

\textbf{Thanks for the good comment. As suggessted, we have added more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. Specifically, we evaluate the untargeted and targeted attack performance on the following datasets and metrics: (1) AO and precision on OTB2015, (2) SR and AO on GOT-Val, and (3) precision, normalized precision and AO on LaSOT.
% 新增加的实验结果分析位于某处，展示如下。
The detailed analysis of new added experiments is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

@@

\uline{
$A_{\text{paste}}$ means that, in the region where the perturbation is pasted, the pixel values of the original image are \textit{replaced} with the pixel values of the perturbation.
The operator $A_\text{add}$ refers to the injection of our translucent adversarial patch into the search image, \ie, the values of our translucent adversarial patch are \textit{added} to the pixel values of the original image in the $b^{fake}_{\textbf{x}}$ area.}

\uline{
The adversarial patch is usually added to the background region of the search image and does not change the pixel values in the foreground region where the real target exists. Therefore if we do not add additional perturbation to the template image, the response values of the region where the real target exists on the heatmaps are always high. Thus it is necessary to perturb the template image to cooling down hot regions where the real target exists on the heatmaps and increasing the responses at the position of the \textit{fake target}.
}

%%%% 问题 2.2 %%%%
\textit{2. I agree with reviewer 3, the ground truth boxes are inaccessible to trackers during the inference. It seems that the authors use the ground truth boxes to generate the fake trajectory in lines 51-57 on page 7. Please clarify it.}

\textbf{
Thanks for the good comment. As suggested, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes.
% 描述轨迹：一段视频中方向是固定的，不同视频中的方向随机挑一个。
Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

@@

\begin{table}[t]
  \renewcommand\thetable{VIII}
  \centering
  \caption{Influence of different ways to generate the fake trajectory.
  The first row represents that the attacker forces the tracker to follow a fixed direction in a video.
  The second row represents that the fake trajectory follows the real trajectory. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real trajectory      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

%%%% 问题 2.3 %%%%
\textit{3. For the experiments, the authors should conduct the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.}

\textbf{Thanks for your advice and we have conducted the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

@@

\uline{We utilize this Iterative Target Class Method to update our perturbation values during the training process. To achieve a balance between the attack efﬁciency and the perturbation perceptibility, we constrain the perturbation values in the loss function of Eq.~(10) instead of using the clip operation. At each training step, our perturbations are updated as follows:}
\begin{gather}
\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)\\
p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L),
\end{gather}

\textit{3. The descriptions of figures and tables are not self-explanatory.}

\textbf{Thanks for your advice and we have replaced the descriptions of figures and tables. The modification is shown as follows for the convience of cross checking.}

% table 2
\textbf{In Table II, we have replaced ``Compared with baselines on perturbed GOT-Val dataset.'' with}
\uline{``Comparison of attack performance with 2 baseline methods on GOT-Val in terms of AO. Baseline1 performs untargeted attacks based on the UAP \cite{UAP} method. Baseline2 performs targeted attacks based on the adversarial patch \cite{patch} method.''}
\textbf{in Section IV.D of the revised manuscript.}

% table 6
\textbf{In Table VI, we have replaced ``Contribution of each loss on GOT-Val.'' with}
\uline{``Analysis of the impact of each loss component on GOT-Val.''}
\textbf{in Section IV.E of the revised manuscript.}

% table 12
\textbf{In Table XII, we have replaced ``Transferability to different backbones on GOT-Val.'' with}
\uline{``Transferability to different backbones on GOT-Val. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more different backbones of SiamFC++, i.e., ShuffleNet \cite{ShuffleNet} and AlexNet \cite{AlexNet}.''}
\textbf{in Section IV.F of the revised manuscript.}

% table 13
\textbf{In Table XIII, we have replaced ``Transferability to different tracking architectures on OTB2015.'' with}
\uline{``Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to three more state-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}.''}
\textbf{in Section IV.F of the revised manuscript.}

% table 14
\textbf{In Table XIV, we have replaced ``Untargeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of untargeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

% table 15
\textbf{In Table XV, we have replaced ``Targeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of targeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

@@

\textit{5. Some of the experiments require more explanations. For example, transferability has been investigated by different backbones \& architectures. It's needed to mention these experiments are with/without the training phase or not.}

\textbf{Thanks for the good comment. These experiments do not need the training phase and we have clarified this in Section IV.F of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

@@

\uline{In this sub-section, we analyze the transferability of the proposed attack method. Specifically, the perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to other tracking networks including SiamFC++\_ShuffleNet, SiamFC++\_\\AlexNet, SiamPRN, SiamRPN++ and Ocean.}

\textit{6. In experiments, I suggest considering two scenarios of different directions and trajectories.}

\textbf{Thanks for the good comment. As suggest, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes. Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Many thanks for your positive comments on the strength of our paper and the novelty of the proposed attack method.}

%%%% 问题 1.1 %%%%
\textit{In addition, I suggest the authors add more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. The experimental results show that it is effective to use the predicted boxes instead of ground truth boxes for training perturbations.}

\textbf{Thanks for the good comment. As suggessted, we have added more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. Specifically, we evaluate the untargeted and targeted attack performance on the following datasets and metrics: (1) AO and precision on OTB2015, (2) SR and AO on GOT-Val, and (3) precision, normalized precision and AO on LaSOT.
% 新增加的实验结果分析位于某处，展示如下。
The detailed analysis of new added experiments is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\begin{table}[t]
  \renewcommand\thetable{X}
  \centering
  \caption{Attack results on OTB2015, GOT-Val and LaSOT with or without the groundtruth information.% w/ GT represents that we train perturbations using the groud truth bounding box information of the trainig dataset. w/o GT represents that we train perturbations using the predicted boxes instead of ground truth boxes of the training dataset.
  }
  \begin{tabular}{rrcccc}
  \toprule
  \multirow{2}{*}[-2pt]{Benchmarks} & \multirow{2}{*}[-2pt]{Metrics} & \multicolumn{2}{c}{Unargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                              &                          & w/ GT  & \multicolumn{1}{l}{w/o GT}  & w/ GT  & \multicolumn{1}{l}{w/o GT} \\ \midrule
  \multirow{2}{*}{OTB2015}     & AO                       & 0.063  & 0.056                       & 0.759  & 0.752                      \\
                              & Precision                & 0.092  & 0.080                       & 0.795  & 0.794                      \\ \midrule
  \multirow{2}{*}{GOT-Val}    & SR                       & 0.123  & 0.121                       & 0.890  & 0.893                      \\
                              & AO                       & 0.153  & 0.160                       & 0.840  & 0.833                      \\ \midrule
  \multirow{3}{*}{LaSOT}      & Precision                & 0.046  & 0.043                       & 0.605  & 0.531                      \\
                              & Norm. Prec.              & 0.048  & 0.044                       & 0.702  & 0.660                      \\
                              & AO                       & 0.069  & 0.063                       & 0.691  & 0.646                      \\ \bottomrule
  \end{tabular}
  \label{tab:agent_GT}
\end{table}

@@

%%%% 问题 2.2 %%%%
\textit{2. I agree with reviewer 3, the ground truth boxes are inaccessible to trackers during the inference. It seems that the authors use the ground truth boxes to generate the fake trajectory in lines 51-57 on page 7. Please clarify it.}

\textbf{
Thanks for the good comment. As suggested, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes.
% 描述轨迹：一段视频中方向是固定的，不同视频中的方向随机挑一个。
Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\uline{
% 介绍轨迹生成方式
\textit{Ablation Study: An alternative way to generate the fake trajectory}  Here, we consider an alternative way to generate the \textit{fake trajectory}. Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
% 分析实验结果。简单分析即可。
As shown in Table \ref{table:direction}, our attack algorithm achieves effective attacks under two different fake trajectories. Specifically, when the fake trajectory follows a fixed direction, the AO of the untargeted attack is 0.175, and the AO of the targeted attack is 0.845.
}

\begin{table}[t]
  \renewcommand\thetable{XI}
  \centering
  \caption{Influence of two different ways to generate the fake trajectory: following a fixed direction in each video and following the real trajectory. It is evaluated on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real trajectory      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

@@

%%%% 问题 2.3 %%%%
\textit{3. For the experiments, the authors should conduct the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.}

\textbf{Thanks for your advice and we have conducted the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\uline{\textit{Ablation Study: Only perturb the template or search image} To analyze the impact of $p$ and $\delta$, we evaluate the attack performance when only adding perturbations on the template images or the search regions.
The attack performance is evaluated according to AO/SR on GOT-Val.
The result is shown in Table \ref{table:one_branch}.
% 对比无目标攻击性能。
For the untargeted attack, only perturbing the template/search image leads to the AO of 0.510/0.714, while perturbing both the template and the search image leads to the AO of 0.153.
% 有目标
For the targeted attack, only perturbing the template/search image leads to the AO of 0.156/0.160, while perturbing both the template and the search image leads to the AO of 0.840. Experimental results show that perturbing both the template and the search image can achieve better attack performance than only perturbing the template/search image.}

\begin{table}[t]
  \renewcommand\thetable{VIII}
  \centering
  \caption{Attack performance comparison when only adding the perturbation on the search/template image. It is evaluated on GOT-Val.}
  \label{table:one_branch}
  \begin{tabular}{@{}cccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Template} & \multirow{2}{*}[-2pt]{Search} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                                  &                               & AO                & SR                & AO               & SR               \\ \midrule
  \checkmark                      &                               & 0.510             & 0.567             & 0.156            & 0.106            \\
                                  & \checkmark                    & 0.714             & 0.841             & 0.160            & 0.132            \\
  \checkmark                      & \checkmark                    & 0.153             & 0.123             & 0.840            & 0.890            \\
  \bottomrule
  \end{tabular}
\end{table}

@@

%%%% 问题 2.4 %%%%
\textit{4. As reviewer 1 and reviewer 2 say, the perturbations added to template regions and research regions are not imperceptible, which may be helpful to misguide the tracker. The reviewer considers that adding a similar random pattern on the template and search regions to further illustrate the effectiveness of the proposed method.}

\textbf{To illustrate the effectiveness of the proposed method, we add random patterns on the template and search regions. 
Specifically, we design two kinds of random patterns: (1) the random pattern similar to the trained perturbations, and (2) the random pattern generated using zero-mean Gaussian noise with standard deviation 50.0.
We replace the trained perturbations with the random random pattern to attack SiamFC++\_GoogleNet. The experiment is performed on GOT-Val.
As shown in Table \ref{table:noise}, random patterns cannot effectively attack the tracker.
For your convenience in cross-checking, the new text is given as follows.
}

\begin{table}[t]
  \renewcommand\thetable{VII}
  \centering
  \caption{Attack performance comparison using other random patterns. It is evaluated on GOT-Val.}
  \label{table:noise}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Perturbations used to \\ perfrom attack \end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack}\\ \cmidrule{2-5}
                                                         & AO                                      & SR                               & AO                & SR                  \\ \midrule
  Trained Perturbations                                  & 0.153                                   & 0.123                            & 0.840             & 0.890               \\
  Similar Pattern                                         & 0.736                                   & 0.871                            & 0.153             & 0.118               \\
  Gaussian Noise                                         & 0.740                                   & 0.875                            & 0.144             & 0.101               \\ \bottomrule        
  \end{tabular}
\end{table}
\begin{figure}[t]
  \renewcommand\thefigure{9}
  \centering
  \includegraphics[width=0.8\textwidth]{images_imperceptible/random_gaussian.pdf}
  \caption{Visualization of the manually generated similar random patterns.}
  \label{fig:random}
\end{figure}
\uline{\textit{Ablation Study: Attack performance of random patterns} To illustrate the effectiveness of the proposed method, we add random patterns on the template and search regions (see Figure \ref{fig:random}). 
Specifically, we design two kinds of random patterns: (1) the random pattern similar to the trained perturbations, and (2) the random pattern generated using zero-mean Gaussian noise with standard deviation 50.0.
We replace the trained perturbations with the random random pattern to attack SiamFC++\_GoogleNet. The experiment is performed on GOT-Val.
As shown in Table \ref{table:noise}, random patterns cannot effectively attack the tracker.
}

@@

\textbf{
Thanks for your advice.
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在$64 \times 64$这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\begin{figure}[t]
  \renewcommand\thefigure{8}
  \centering
  \includegraphics[width=.8\textwidth]{images_imperceptible/1.pdf}
  \caption{Visualization of the perturbations in attacking the different RGB and YCbCr color spaces. Note that the perturbation of the search image in the Y channel results in SSIM value of 0.95 outside the added patch area, which slightly deteriorate the imperceptibility.}
  \label{fig:YCbCr}
\end{figure}

\begin{table}[t]
  \renewcommand\thetable{VI}
  \centering
  \caption{Comparison between attacking the different RGB and YCbCr color spaces. Attacking the YCbCr color space means we first convert the search image into YCbCr color space, and then add a perturbation to the entire search image in the Y channel and a different perturbation to a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Different Color\\ Space Attack\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}

@@

\uline{We utilize this Iterative Target Class Method to update our perturbation values during the training process. To achieve a balance between the attack efﬁciency and the perturbation perceptibility, we constrain the perturbation values in the loss function of Eq.~(10) instead of using the clip operation. At each training step, our perturbations are updated as follows:}
\begin{gather}
\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)\\
p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L),
\end{gather}

\textit{3. The descriptions of figures and tables are not self-explanatory.}

\textbf{Thanks for your advice and we have replaced the descriptions of figures and tables. The modification is shown as follows for the convience of cross checking.}

\textbf{In Table IV, we have replaced ``Compared with baselines on perturbed GOT-Val dataset.'' with}
\uline{``Comparison of attack performance with 2 baseline methods on GOT-Val in terms of AO. Baseline-1 performs untargeted attacks based on the UAP [9] method. Baseline-2 performs targeted attacks based on the adversarial patch [50] method.''}
\textbf{in Section IV.D of the revised manuscript.}

\textbf{In Table IX, we have replaced ``Contribution of each loss on GOT-Val.'' with}
\uline{``Analysis of the impact of each loss component on GOT-Val.''}
\textbf{in Section IV.E of the revised manuscript.}

\textbf{In Table XII, we have replaced ``Transferability to different backbones on GOT-Val.'' with}
\uline{``Transferability to different backbones of our perturbations trained on SiamFC++\_GoogleNet. It is evaluated on GOT-Val.''}
\textbf{in Section IV.F of the revised manuscript.}

\textbf{In Table XIII, we have replaced ``Transferability to different tracking architectures on OTB2015.'' with}
\uline{``Transferability to different tracking architectures of our perturbations trained on SiamFC++\_GoogleNet. It is evaluated on OTB2015.''}
\textbf{in Section IV.F of the revised manuscript.}

@@

% table 14
\textbf{In Table XIV, we have replaced ``Untargeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of untargeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

% table 15
\textbf{In Table XV, we have replaced ``Targeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of targeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

% figure 4
\textbf{In Figure 4, we have replaced ``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} (indicated by the yellow targeted bounding box).'' with}
\uline{``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} $B^{fake}=\{b^{fake}_i\}_1^{T}$ (indicated by the yellow bounding boxes). The \textit{fake trajectory} follows the real trajectory $B^{gt}=\{b^{gt}_i\}_1^T$ (indicated by the red bounding boxes) except that the adjacent boundaries of $b^{fake}_i$ and $b^{gt}_i$ are 2 pixels apart.''}

@@

\textit{6. In experiments, I suggest considering two scenarios of different directions and trajectories.}

\textbf{Thanks for the good comment. As suggest, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes. Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\uline{\textit{Ablation Study: An alternative way to generate the fake trajectory} Here, we consider an alternative way to generate the \textit{fake trajectory}. Specifically, the attacker forces the tracker to follow a fixed direction in a video. For each video, we assign a random direction from 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
% 分析实验结果。简单分析即可。
As shown in Table \ref{table:direction}, our attack algorithm achieves effective attacks under two different fake trajectories. Specifically, when the fake trajectory follows a fixed direction, the AO of the untargeted attack is 0.175, and the AO of the targeted attack is 0.845.}

\begin{table}[t]
  \renewcommand\thetable{\ref{table:direction}}
  \centering
  \caption{Influence of two different ways to generate the fake trajectory: following a fixed direction in each video and following the real trajectory. It is evaluated on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real trajectory  & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
\end{table}

@@

\textbf{We have discussed several state-of-the-art anchor free Siamese trackers at the related work. For your convenience of cross review, the new text is given as follows.}

\uline{In this anchor-free paradigm, many recent works (e.g., \cite{zhang2020ocean}, \cite{cui2020fully}, \cite{9157720}) are dedicated to more robust and efficient visual tracking based on various anchor-free settings.
% Ocean
Ocean \cite{zhang2020ocean} directly predicts the position and scale of target objects in an anchor-free fashion; since each sample position in groundtruth boxes is well trained, the tracker is capable of rectifying inexact predictions of target objects during inference.
% FCOT
FCOT \cite{cui2020fully} introduces an online regression model generator (RMG) based on the carefully designed anchor-free box regression branch, which enables the tracker to be more effective in handling target deformation during tracking procedure.
%  SiamCAR
SiamCAR \cite{9157720} is both anchor and proposal free, and takes one unique response map to predict object location and bounding box directly; this setting significantly reduces the number of hyper-parameters, which keeps the tracker from complicated parameter tuning and makes the tracker significantly simpler, especially in training.
}

\textbf{Besides, we have evaluated the transferability to the anchor free tracker OCEAN in Setcion IV.E of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\begin{table}[t]
  \renewcommand\thetable{XIII}
  \centering
  \caption{Transferability to different tracking architectures of our perturbations trained on SiamFC++\_GoogleNet. It is evaluated on OTB2015.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO    & Precision \\ \midrule
  SiamRPN++ [24]            & 0.676   & 0.879             & 0.418 & 0.556     \\
  SiamRPN [23]              & 0.666   & 0.876             & 0.483 & 0.643     \\
  Ocean [20]                & 0.672   & 0.902             & 0.237 & 0.282     \\ \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
\uline{\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to three more tate-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}. SiamRPN and SiamRPN++ are ahchor-based trackers, and Ocean is an anchor-free tracker. The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.483 and the performance of SiamRPN++ is decreased from 0.676 to 0.418. In the case of Ocean, the AO with respect to the \textit{real trajectory} drops from 0.902 to 0.282. The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.
}
